Revisited hidden weight bit function

### 2024-10-29 RevisedHiddenWeight.tex
git

The $n$-variable \emph{Boolean symmetric functions} are those that are constant on each slice $\Ekn{k}{n}$ for $k\in [0,n]$. 
This class has been assiduously studied in the context of cryptography, see \eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,IEEE:CheLu11,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
In this article we mainly consider the slice indicator functions.
%\begin{definition}[Elementary symmetric functions]
%Let $i\in [0,n]$, the elementary symmetric function of degree $i$ in $n$ variables, denoted $\sigma_{i,n}$, is the function which ANF contains all monomials of degree $i$ and no monomials of other degrees. 
%\end{definition}
\begin{definition}[Slice indicator functions]\label{def:slice}
 Let $k\in [0,n]$, the indicator function of the slice of weight $k$ is defined as:
 \[\forall  x\in \mathbb{F}_2^{n}, \quad \phikn{k}{n}(x) = 1 \text{ if and only if } \w(x) = k.\]
\end{definition}

@@

\pmnote{complete the following prop, + references}

\begin{Prop}[Cryptographic properties of functions from $\WD{1}{n}$ \label{prop:wwd1}]
Let $n\in \N^*$, the following hold for functions in $\WD{1}{n}$.
\begin{itemize}
	\item Nonlinearity of majority functions.
	\item Nonlinearity of HWBF.
	\item Nonlinearity bound WWA.
\end{itemize}

>>>>

The $n$-variable \emph{Boolean symmetric functions} are those that are constant on each slice $\Ekn{k}{n}$ for $k\in [0,n]$. 
This class has been assiduously studied in the context of cryptography, see \eg \cite{IEEE:Carlet04,IEEE:CanVid05,INDO:BraPre05,DM:SarMai07,IEEE:QFLW09,IEEE:CheLu11,Latin:Meaux19,CCDS:Meaux21,IEEE:CarMea21}.
In this article we mainly consider the slice indicator functions and the majority functions.
%\begin{definition}[Elementary symmetric functions]
%Let $i\in [0,n]$, the elementary symmetric function of degree $i$ in $n$ variables, denoted $\sigma_{i,n}$, is the function which ANF contains all monomials of degree $i$ and no monomials of other degrees. 
%\end{definition}
\begin{definition}[Slice indicator functions]\label{def:slice}
 Let $k\in [0,n]$, the indicator function of the slice of weight $k$ is defined as:
 \[\forall  x\in \mathbb{F}_2^{n}, \quad \phikn{k}{n}(x) = 1 \text{ if and only if } \w(x) = k.\]
\end{definition}

\pmnote{add}
\begin{definition}[Majority functions]\label{def:maj}
\end{definition}

@@

\pmnote{complete the following prop. Choose between nonlinearity or $\max_{a\in\mathbb F_2^n}|\wt f(a)|$}

\begin{Prop}[Cryptographic properties of functions from $\WD{2}{n}$ \label{prop:wwd1}]
Let $n\in \N^*$ even, the following hold for functions in $\WD{2}{n}$. 
\begin{itemize}
	\item For the majority function

	$\max_{a\in\mathbb F_2^n}|\wt f(a)|$ (adapt from Theorem 3 \cite{DCC:DalMaiSar06})
	\item value for HWBF. (from~\cite{DAM:WCST14}))

	\item  bound for the cyclic weightwise linear (adapt Theorem 1 of \cite{DAM:MeaOza24})
	\item  bound for the cyclic weightwise quadratic function $t$  (adapt Theorem 2 of \cite{DAM:MeaOza24})
\end{itemize}
